---
title: "ProgAssg_Week4"
author: "Sathish"
date: "March 11, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##Background
The World's Telephones

###<b>Description</b>
The number of telephones in various regions of the world (in thousands). The regions are: North America, Europe, Asia, South America, Oceania, Africa, Central America. The years are: 1951, 1956, 1957, 1958, 1959, 1960, 1961.

###<b>Source</b>
AT&T (1961) The World's Telephones.

###<b>References</b>
McNeil, D. R. (1977) Interactive Data Analysis. New York: Wiley.

##Summary
The App allows user to browse different regions (continents) and plots the number of phones (in thousands) vs. year and fits a best fit curve using "loess" method.

##Server Code {.smaller}
```{r echo = TRUE}
# Load libraries
suppressMessages(library(ggplot2))
suppressMessages(library(reshape2))

phoneplot <- function (region)
{
    # Make a narrow data set
    WP <- melt(WorldPhones)
    colnames(WP) <- c("Year","Region","Phones")
    
    # Select only rows for selected region
    WP <- WP[which(WP$Region == region),]
    
    # Plot no. of phones vs. time for selected region
    p <- ggplot(WP,aes(x=Year,y=Phones)) +
        labs(x="Year",y="Number of Phones (in thousands)") + 
        geom_point(size=4) + geom_smooth()
    return(p)
}
```

##Sample Plot {.smaller}
```{r WorldPhones, echo = TRUE}
phoneplot("Asia")
```

##Thank you

